\fakebf{HIV virulence evolution in structured epidemic models}

### 2016-05-31 poster/hivlhs_eeid2016.Rnw
final?? poster

\begin{itemize}

\item least (random) and most (pairform+epc) models \textbf{most similar}:
  single individuals and extra-pair contact wash out effects of structure
\item implicit model is \textbf{most different}
\item random-mixing model underestimates variability
\end{itemize}

@@

\begin{block}{Sensitivity}
<<sens,dev="png",echo=FALSE,fig.width=20,fig.height=10,cache=TRUE>>=
mL3 <- subset(mL2,
       !((model=="implicit" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="random" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="instswitch" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="instswitch+epc" &
          LHSvar %in% c("rho_base","c_u_ratio")) |
         (model=="pairform" &
          LHSvar %in% c("c_u_ratio","c_e_ratio"))))
## reorder factors
mL3$LHSvar <- factor(mL3$LHSvar,
                     levels=c("Beta1","Beta3",
                              "Duration1","Duration3",
                              "c_mean_base","c_e_ratio","rho_base",
                              "c_u_ratio"),
                     labels = c("beta[P]", "beta[D]", "D[P]", "D[D]",
                                "c", "c[e]/c[w]", "rho", "c[u]/c[w]"))

>>>>

\begin{itemize}
\item \textbf{80\% of total variability} in peak SPVL is among- vs. within-model
\item least (random) and most (pairform+epc) models \textbf{most similar}:
  single individuals and extra-pair contact wash out effects of structure
\item implicit model is \textbf{most different}
\item random-mixing model underestimates variability
\end{itemize}

@@

\begin{block}{Sensitivity}
<<sens,dev="png",echo=FALSE,fig.width=20,fig.height=10,cache=TRUE,out.width="0.95\\textwidth">>=
mL3 <- subset(mL2,
       !((model=="implicit" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="random" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="instswitch" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="instswitch+epc" &
          LHSvar %in% c("rho_base","c_u_ratio")) |
         (model=="pairform" &
          LHSvar %in% c("c_u_ratio","c_e_ratio"))))
## reorder factors
mL3$LHSvar <- factor(mL3$LHSvar,
                     levels=c("Beta1","Beta3",
                              "Duration1","Duration3",
                              "c_mean_base","c_e_ratio","rho_base",
                              "c_u_ratio"),
                     labels = c("beta[P]", "beta[D]", "D[P]", "D[D]",
                                "c", "c[e]/c[w]", "rho", "c[u]/c[w]"))
